---
title: "Stat 159 Final Project - Providing Credit to Students"
author: "TEAM W.O.S: Young Hoon Kim, Yoon Jung Rho,Joseph Simonian, Ellen Hwang"
date: "December 2, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

methods,results, analysis, conclusion, thank you slide



# Client Profile

## Client Profile 

Our client is a credit institution that provides financial aid to students. The managers are interested in expanding their customer base but they would also like that most of the loans be payed back.

Main Question: What features and details of a school make it reliable for credit?

# Data

## Data

1. [College Scorecard](https://ed-public-download.apps.cloud.gov/downloads/CollegeScorecard_Raw_Data.zip): data on student completion, debt and repayment, earnings, and more. The files include data from 1996 through 2016 for all undergraduate degree-granting institutions of higher education. This data was last updated on September 13th, 2016.
2. [Post-school earnings](https://ed-public-download.apps.cloud.gov/downloads/Most-Recent-Cohorts-Treasury-Elements.csv): more current and detailed information about student post-school earnings for all undergraduate degree-granting institutions of higher education


Complete College Scorecard Data is available at https://collegescorecard.ed.gov/data/

Documentation on all data is available at https://collegescorecard.ed.gov/data/documentation/

# Methods

## Methods

```{r results = "asis", echo = FALSE}
load("../data/RData/correlation.RData")
knitr::kable(high_cor_rpy3yr_tbl, caption = "Variables with Greater than .5 Correlation with Repayment Rate")

```

# Results

# Analysis

# Conclusion

# Thank You!